\stktokens{}: Enforcing Well-Bracketed Control Flow and Stack Encapsulation Using Linear Capabilities

### 2019-07-27 popl-2019-journal-v/proving-full-abstraction.tex
[POPLjv] implement comment about sharedWorld

This is expressed by stripping the world of all its ownership which corresponds to replacing all $\spatialo$ regions with $\spatial$ regions.
\todo[inline]{Dominique: step missing in the reasoning: expressing that the capability is not linear is done by stripping the world ... \emph{and then} requiring that the capability is valid w.r.t.\ this stripped world.}

>>>>

This is expressed by stripping the world of all its ownership which corresponds to replacing all $\spatialo$ regions with $\spatial$ regions and then requiring that the capability is valid w.r.t.\ this new world.
